%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.


\indent 
I would like to express my most sincere gratitude to my advisor, Dr. Casey Papovich, for the continual support of my research pursuits, his unwavering patience, the kind and sometimes stern words, his encouragement, and vast knowledge. His support and guidance have helped me throughout all stages of researching and writing this dissertation. I can confidently say that I would not have arrived alone, and I cannot imagine a better advisor for my study.

To my dissertation committee: Dr. Wolfgang Bangerth, Dr. Louis Strigari, and Dr. Nicholas Suntzeff who were always at the ready with invaluable comments and encouragement, and for never shying away from asking the hard questions which pushed me to new heights. Thank you.

I thank my fellow graduate students with whom I spent so much of my life. Thank you for all the stimulating discussions, homework and research help, encouragement, and the fun over the previous six years.

Finally, I could not have accomplished this without the love and support of my family and friends. I am so very fortunate that there are too many to name, but thank you for always believing in me, even when I did not believe in myself. Thank you for being a distraction when I needed it, and for being a support system when I needed it. Thank you for your unwavering optimism, and your tireless work. I can never repay you. Thank you.
\pagebreak{}